\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{listings}
\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Octave,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\newtheorem{theorem}{Theorem}
\newtheorem{es}{Examples}

\begin{document}

\lstinputlisting{p2-RecPowerTwo.py}

\begin{theorem}
    Assuming the precondition holds before the execution of the program, RecPowerTwo
    will terminate and the postcondition holds.
\end{theorem}

\textbf{Proof:}

First, we will prove the following predicate: For all $i\in\mathbb{N}$, let $P(i)$ be the predicate:
\[ P(i):\qquad\text{The function call RecPowerTwo(i) returns $2^i$} \]
Base Case: i = 0. We fulfill the condition on line 4 since i = 0 so, by line 5, RecPowerTwo puts
the value of result at 1 and then exits. Since $2^0 = 1$, we are done.
Assume that P(i) holds. We want to show P(i + 1) holds.
Assume RecPowerTwo(i + 1) is called. Since $i \in N, i + 1 > 0$ holds so the condition on line 4 is
not fulfilled. Thus the program skips to line 6 where the function call RecPowerTwo(i) is called.
By our induction hypothesis, P(i) holds and so RecPowerTwo(i) returns $2^i$. Thus, we have:
\[ \text{result}\; = 2 * 2^i \]
and so result$ = 2^{i+1}$. Thus, the program terminates and returns $2^{i+1}$ as wanted. Therefore,
P(i+1) holds as wanted.\\

The predicate shows the program terminates and the value which it returns satisfies the postcondition
so we are done.

\end{document}
